R tools for accessing research literature for text mining

### 2019-08-23 manuscript.Rmd
fix #17 dont need tidy actually

Since users can go through a lot of article requests, we cache successfully
downloaded articles, and keep that knowledge consistent across R sessions; all
subsequent requests for the same article just use the cached version. Additionally,
all errors in `ft_get()` are collected in a tidy data.frame in the output of the
function to help the user quickly determine what went wrong.

>>>>

Since users can go through a lot of article requests, we cache successfully
downloaded articles, and keep that knowledge consistent across R sessions; all
subsequent requests for the same article just use the cached version. Additionally,
all errors in `ft_get()` are collected in a data.frame in the output of the
function to help the user quickly determine what went wrong.
